Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2016-08-09 Docs/IJES/journal.tex
[A-13] In page 6 (left column), please, rewrite the last sentence in Section 4.2: "In the ... ? is not ...".

\lstset{language=C,basicstyle=\small}
\lstset{numbers=left, numberstyle=\tiny, stepnumber=1, numbersep=5pt}
\lstset{tabsize=2}
\lstset{firstnumber=1}
\lstset{frame=single}
\lstset{
  language={C},
  morekeywords={assert,uchar}
}

@@

@@

\begin{lstlisting}[basicstyle=\footnotesize,caption={Pseudocode describing sequential ESBMC.},label={Pseudocode-describing-ESBMC},numbersep=7pt,frame=tb,captionpos=t,numberstyle=\tiny,mathescape=true]
Initialize variables 
Declare number of nodes and edges
Declare hardware cost of each node as array (h)
Declare software cost of each node as array (s)
Declare communication cost of each edge (c)
Declare the initial sw cost of ($S_0$)
Declare transposed incidence matrix graph G(E)
Define the solutions ($x_i$) as Boolean
main {
 For TipH = 0 to Hmax Do {
  Populate $x_i$ with nondet (the values of test)
  Calculate s_i(1-x_i)+c|Ex_i| and store at variable
  Requirement enforced by Assume (variable <= $S_0$)
  Calculate Hp cost Based on value of $x_i$
  Violation check with Assert(Hp > TipH)
 }
}
\end{lstlisting}

@@

A loop controls the cost of hardware hint, starting with zero and reaching the maximum value considering the case, where all nodes are partitioned to hardware (Hmax). To every test performed, the hardware hint is compared to the feasible solution. This is accomplished by an \textit{ASSERT} statement at the end of the algorithm, a predicate that controls the halt condition (a \textit{true-false} statement). If the predicate is \textit{FALSE}, then the optimization is finished, {\it i.e.}, the solution is found.

@@

In the ESBMC algorithm is not necessary to add slack variables at Eq.~\eqref{hw-sw-partitioning}, which reduces the number of variables to be solved when compared to ILP and GA.

>>>>

\lstset{language=C,basicstyle=\small}
\lstset{numbers=left, numberstyle=\tiny, stepnumber=1, numbersep=5pt}
\lstset{tabsize=2}
\lstset{firstnumber=1}
\lstset{frame=single}
\lstset{
  language={C},
  morekeywords={assert,uchar,assume,For,do}
}

@@

\textcolor{red}{Conforme mencionado pelo revisor, falta definir o indice ``i''.}

@@

\begin{lstlisting}[basicstyle=\footnotesize,caption={Pseudocode describing sequential ESBMC.},label={Pseudocode-describing-ESBMC},numbersep=7pt,frame=tb,captionpos=t,numberstyle=\tiny,mathescape=true]
Initialize variables 
Declare number of nodes and edges
Declare the maximum hardware cost ($H_{max}$)
Declare hardware cost of each node as array ($h$)
Declare software cost of each node as array ($s$)
Declare communication cost of each edge ($c$)
Declare the initial sw cost of ($S_0$)
Declare transposed incidence matrix graph $G(E)$
Define the decision variables ($x_i$) as Boolean
main {
 For $TipH=0$ to $H_{max}$ do {
  Populate $x_i$ with non-deterministic values
  Calculate $s_i(1-x_i)+c|Ex_i|$ and store in variable
  Requirement enforced by assume(variable $\leq$ $S_0$)
  Calculate $H_p$ cost based on value of $x_i$
  Violation check with assert($Hp > TipH$)
 }
}
\end{lstlisting}

@@

A loop controls the cost of hardware hint, starting with zero and reaching the maximum value considering the case, where all nodes are partitioned to hardware ($H_{max}$). To every test performed, the hardware hint is compared to the feasible solution. This is accomplished by an \textit{ASSERT} statement at the end of the algorithm, a predicate that controls the halt condition (a \textit{true-false} statement). If the predicate is \textit{FALSE}, then the optimization is finished, {\it i.e.}, the solution is found.

@@

In the ESBMC algorithm, there is no need for adding slack variables in Eq.~\eqref{hw-sw-partitioning}, which reduces the number of variables to be solved if compared to ILP and GA.
